Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/motivation.tex
typo

These input processing vulnerabilities fall into two broad classes.  The first
class, of occurred 11 times, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers of lower-level languages avoid these bugs
in the first place.

>>>>

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers of lower-level languages avoid these bugs
in the first place.
